### 2015-07-13 narrative/enabling_tech.tex

From the user perspective,
{\bf ADIOS}~\cite{liu_helloadios,lofstead:2009:adaptible} offers an API nearly as simple as POSIX, but with the
ability to change the actual data transport mechanism without changing the
source code. This flexibility allows users to shift from writing data to a file system
to operating on data with in situ techniques without changing the source code.
ADIOS has proven effective for writing to POSIX file
systems~\cite{lofstead:2009:adaptible}, data staging systems~\cite{zheng:2010:predata,docan:2010:dataspaces,oldfield:2006:nessie}, workflow
systems~\cite{Dayal:2014:flexpath}, and even through the WAN network~\cite{zhang2014active}. Further,
I/O rerouting and throttling techniques \cite{liu_hotstorage,liu_helloadios} have been developed 
within ADIOS to reduce contentions on best-effort storage systems. This is our initial
effort in tackling storage load imbalance and improving storage QoS on current DOE systems.
Part of this project's goals are to understand where the dividing line
between the storage layer shared by all users and middleware being used by a
single or small number of users. We will utilize DataSpaces~\cite{docan:2010:dataspaces} to 
further integrate the I/O (ADIOS) layer with the storage layer (Sirocco).
%
% 
%They offer a way to request data set portions
%from a one component by the next componet in a data flow. In DataSpaces case,
%the data transfer does not have to correspond to the data from a single
%process.  Instead, DataSpaces will determine where the data is and issue
%requests to pull the data from the source to the sink in an on demand process.

>>>>

From the user perspective,
{\bf ADIOS}~\cite{liu_helloadios,lofstead:2009:adaptible} offers an API nearly as simple as POSIX, but with the
ability to change the actual data transport mechanism without changing the
source code. This flexibility allows users to shift from writing data to a file system
to operating on data with in situ techniques without changing the source code.
ADIOS has proven effective for writing to POSIX file
systems~\cite{lofstead:2009:adaptible}, data staging systems~\cite{zheng:2010:predata,docan:2010:dataspaces,oldfield:2006:nessie}, workflow
systems~\cite{Dayal:2014:flexpath}, and even through the WAN network~\cite{zhang2014active}. Further,
I/O re-routing and throttling techniques \cite{liu_hotstorage,liu_helloadios} have been developed 
within ADIOS to reduce contentions on best-effort storage systems. This is our initial
effort in tackling storage load imbalance and improving storage QoS on current DOE systems.
Part of this project's goals are to understand where the dividing line
between the storage layer shared by all users and middleware being used by a
single or small number of users. We will utilize DataSpaces~\cite{docan:2010:dataspaces} to 
further integrate the I/O (ADIOS) layer with the storage layer (Sirocco).
%
% 
%They offer a way to request data set portions
%from a one component by the next component in a data flow. In DataSpaces case,
%the data transfer does not have to correspond to the data from a single
%process.  Instead, DataSpaces will determine where the data is and issue
%requests to pull the data from the source to the sink in an on demand process.

### 2015-07-13 narrative/evaluation.tex

Our guiding principles are the basis for the evaluation. These principles are
described in Table~\ref{table:eval}, and we will partition the problem along these
lines and evaluate how the knowledge centric system design we employ can
provide more predictable performance and data quality. 
In addition to benchmarking the various SIRIUS methods and tools in isolation,
we will work with our science partners at Princeton University (J. Tromp, C. S. Chang),
and U. C. Irvine (Z. Lin), along with the OLCF and SNL,
to evaluate their applications working with the storage system to
determine performance predictability and data quality.  Our evaluation 
will use the multiple storage layers available on systems at both SNL and the
OLCF, including the sith cluster discussed in the Equipment appendix. 
 We will perform tests in both the system level (on sith) and in
the user level (on titan), and evaluate our results using our application
knowledge.

>>>>

Our guiding principles are the basis for the evaluation. These principles are
described in Table~\ref{table:eval}, and we will partition the problem along these
lines and evaluate how the knowledge centric system design we employ can
provide more predictable performance and data quality. 
In addition to benchmarking the various SIRIUS methods and tools in isolation,
we will work with our science partners at Princeton University (J. Tromp, C. S. Chang),
and U. C. Irvine (Z. Lin), along with the OLCF and SNL,
to evaluate their applications working with the storage system to
determine performance predictability and data quality.  Our evaluation 
will use the multiple storage layers available on systems at both SNL and the
OLCF, including the Sith cluster discussed in the Equipment appendix. 
 We will perform tests in both the system level (on Sith) and in
the user level (on titan), and evaluate our results using our application
knowledge.
